### 2021-03-04 sections/5-imp.tex
added textual descriptions
message chapter started

    Requested Attributes is a list of attribute keys, the user will have to submit as part of the relationship request.

@@

    Shared Attributes is a list of attribute keys and values, the service provider wakes available to any user interested in requesting this relationship. The service provider has to share a minimal amount of attributes which enable the user to identify it.

@@

    The purpose describes why the user and the service provider want to establish the relationship and why the attributes requested by the user are necessary for it.

@@

The integration tool for the service provider does not understand the content of messages but simply makes the accessible by the system architecture of the service provider. Without additional integration solutions, the service provider has to implement his own solutions for processing the different types of messages. The application provided to the user has a set of messages it understands. The list of messages the application is able to process can be expanded by the identity management provider who develops it.

@@

\paragraph{Security}
The IMP system guarantees, that all information is encrypted and can only be decrypted by identities which are allowed to read it. Only the owner of an identity can manage attributes of his identity. A relationship is established only with the identity presented as part of the relationship request and only the specified attributes are shared. Interactions as part of a relationship are only possible between the identities of the relationship.

@@

\subsubsection{User}
The IMP system enables users to manage one identity and share attributes with multiple service providers. This replaces the need of a user profile for all service providers which take advantage of the IMP service. The user wont have to access multiple websites for managing user profiles but update his identity only through the IMP service.
As attributes can only be shared with service providers as part of a relationship, the user has control of his personal information. Before accepting the relationship, he can see information about the identity of the service provider, like his name, address, phone number and more. The user is also provided with information on why the relationship and request attributes are necessary which helps the user in deciding if he agrees with the necessity of sharing the information. As it is possible to establish multiple relationships with a service provider, each with a different specified reason and list of shared attributes, it is possible for user and service provider to establish a relation for each business process which requires access to personal information. The information therefore can not only be shared with a single service provider but also for an individual process. User and service provider can interact through relationships. Therefore messages can be exchanged and associated to a certain business process.

@@

The IMP system enables the service provider to access personal information of users without the need of hosting a system for identity management. Depending on the price of the IMP solution, this can reduce the cost for operating and maintaining the system architecture. The service provider has to hire less personal, does not have to buy expensive hardware and can more easily scale the performance of his system. As previously described, the user experience can also increase and lead to more customers. Relationships enable service providers to request users to share attributes while specifying the legal reasons for processing the information and to directly interact with them. The IMP system takes over the responsibility for securing personal information of users and interactions with the service provider. As the relationship cannot be deleted without approval of both identities, it can be used as proof of for example contracts or order placements. The IMP system provides tools for integration which minimizes the effort for system providers to start using the IMP system.

@@

The IMP system operates on three domains. The user domain contains systems, the user directly interacts with. This typically are applications on PC or smartphone and websites. The IMP system provides an application for PC and smartphone to the user for accessing IMP services. For simplification, the user is assumed to use only one device which eliminates the need for synchronization of devices. The client enables the user to manage attributes of his identity, to establish relationships, to manage relationships and to interact through relationships.

@@

The operation of IMP systems can be separated in multiple layers. The layers build upon each other (from bottom to top) and provide an increasingly abstract perspective on the functionalities of each component.

@@

As the system architecture of the service provider has no way of knowing when the connector receives a relationship request, he iteratively requests an update from the connector trough its REST interface. The connector responds with the received relationship request. The system architecture of the service provider processes the request in order to decide if it should be accepted. The service provider could for example verify if a relationship with the identity already exists or if the E-mail address is already registered.

@@

The connector sends the relationship response to the IMP server which updates the content and status of the corresponding relationship. It might be possible, that the user retracted the relationship request in the meantime. In this case, the relationship response would be dropped by the IMP server and the connector would be notified.
If however, the IMP server updates the status of the relationship to "established", both IMP client and connector are notified with the final content of the relationship.

After receiving the final relationship established notification, the system architecture of the service provider can store the shared attributes in a database along with the corresponding relationship ID for the newsletter system to access.

@@

Through an established message, user and service provider can exchange messages with any structure and content. However, this only makes sense if both IMP client and system architecture of the service provider can understand the messages. IMP server and IMP connector only take care of the correct routing. The list of messages an IMP client understands can be expanded by the identity management provider. It can therefore be assumed, that the IMP client understands any message service providers often want to exchange. For simplicity, in the following sections, behaviour of the IMP client for newly defined message can be defined at will. Two important types of messages were already defined: Mail Messages and Attribute Change Request-Reply Messages.

@@

It is possible, that in the future, the user wants to change the mail address where he receives the newsletter. As the established relationship remains to be valid, it should not be terminated, but shared attributes should be changed instead.

Through the IMP client, the user can view the corresponding relationship and edit the attributes. After he changed the mail attribute he shares, through routing by the IMP server, the IMP client sends a attribute change request message to the connector. The connector does not understand the content of the message but from which relationship it originated from. As the connector cannot notify the system architecture of the service provider, polling for new messages is required. After the system architecture receives the message, it understands the structure of the message and that the purpose of the message is an attribute change request.

The system architecture evaluates if it accepts the changes and sends a response trough the REST interface of the connector. The system architecture might execute additional processes. In this case, the mail address stored in the database would be updated.

The IMP server receives the response message through the connector and routs it to the IMP client. The IMP client understands the message, updates the value stored as part of the relationship and displays a notification to the user.

@@

If a user has questions about the newsletter, he can send messages to the service provider as part of the relationship. Client sends the mail message to the IMP server which routes it to the connector. The system architecture polls for incoming messages. When the system architecture receives the message, it understands the content and purpose and for example notifies an employee. An employee could be notified through E-Mail and a response from the employee to the mail could automatically sent to the relationship through the REST API of the connector. Connector and IMP server route the message to the IMP client, who understands the message and displays it to the user.

@@

\section{}

>>>>

    Requested Attributes is a list of attribute keys the user will have to submit as part of the relationship request.

@@

    Shared Attributes is a list of attribute keys and values the service provider makes available to any user interested in requesting a relationship. The service provider has to share a minimal amount of attributes which enable the user to identify it.

@@

    The purpose describes why the user and the service provider want to establish the relationship and why the attributes requested from the user are necessary for it.

@@

The integration tool for the service provider does not understand the content of messages but simply makes them accessible by the system architecture of the service provider. Without additional integration solutions, the service provider has to implement his own solutions for processing the different types of messages. The application provided to the user has a set of messages it understands. The list of messages the application is able to process can be expanded by the identity management provider who develops it.

@@

\paragraph{Security}
The IMP system guarantees that all information is encrypted and can only be decrypted by identities which are allowed to read it. Only the owner of an identity can manage attributes of his identity. A relationship is established only with the identity presented as part of the relationship request and only the specified attributes are shared. Interactions as part of a relationship are only possible between the identities of the relationship.

@@

\subsubsection{User}
The IMP system enables users to manage one identity and share attributes with multiple service providers. This replaces the need of a user profile for all service providers which take advantage of the IMP service. The user wont have to access multiple websites for managing user profiles but update his identity only through the IMP service.
As attributes can only be shared with service providers as part of a relationship, the user has control of his personal information. Before accepting the relationship, he can see information about the identity of the service provider, like his name, address, phone number and more. The user is also provided with information on why the relationship and request attributes are necessary which helps the user in deciding if he agrees with the necessity of sharing the information. As it is possible to establish multiple relationships with a service provider, each with a different specified reason and list of shared attributes, it is possible for user and service provider to establish a relationship for each business process which requires access to personal information. The information therefore can not only be shared with a single service provider but also for an individual process. User and service provider can interact through relationships. Therefore messages can be exchanged and associated to a certain business process.

@@

The IMP system enables the service provider to access personal information of users without the need of hosting a system for identity management. Depending on the price of the IMP solution, this can reduce the cost for operating and maintaining the system architecture. The service provider has to hire less staff, does not have to buy expensive hardware and can more easily scale the performance of his system. As previously described, the user experience can also increase and lead to more customers. Relationships enable service providers to request users to share attributes while specifying the legal reasons for processing the information and to directly interact with them. The IMP system takes over the responsibility for securing personal information of users and interactions with the service provider. As the relationship cannot be deleted without approval of both identities, it can be used as proof of for example contracts or order placements. The IMP system provides tools for integration which minimizes the effort for system providers to start using the IMP system.

@@

The IMP system operates on three domains. The user domain contains systems the user directly interacts with. These typically are applications on PC or smartphone and websites. The IMP system provides an application for PC and smartphone to the user for accessing IMP services. For simplification, the user is assumed to use only one device which eliminates the need for synchronization of devices. The client enables the user to manage attributes of his identity, to establish relationships, to manage relationships and to interact through relationships.

@@

The operation of IMP systems can be separated into multiple layers. The layers build upon each other (from bottom to top) and provide an increasingly abstract perspective on the functionalities of each component.

@@

As the system architecture of the service provider has no way of knowing when the connector receives a relationship request, he iteratively requests an update from the connector through its REST interface. The connector responds with the received relationship request. The system architecture of the service provider processes the request in order to decide if it should be accepted. The service provider could for example verify if a relationship with the identity already exists or if the e-mail address is already registered.

@@

The connector sends the relationship response to the IMP server which updates the content and status of the corresponding relationship. It might be possible that the user retracted the relationship request in the meantime. In this case, the relationship response would be dropped by the IMP server and the connector would be notified.
If however, the IMP server updates the status of the relationship to "established", both IMP client and connector are notified with the final content of the relationship.

After receiving the final "relationship established" notification, the system architecture of the service provider can store the shared attributes in a database along with the corresponding relationship ID for the newsletter system to access.

@@

Through an established message, user and service provider can exchange messages with any structure and content. However, this only makes sense if both IMP client and system architecture of the service provider can understand the messages. IMP server and IMP connector only take care of the correct routing. The list of messages an IMP client understands can be expanded by the identity management provider. It can therefore be assumed that the IMP client understands any message service providers often want to exchange. For simplicity, in the following sections, behaviour of the IMP client for newly defined message can be defined at will. Two important types of messages were already defined: Mail Messages and Attribute Change Request-Reply Messages.

@@

It is possible that in the future, the user wants to change the mail address where he receives the newsletter. As the established relationship remains to be valid, it should not be terminated, but shared attributes should be changed instead.

Through the IMP client, the user can view the corresponding relationship and edit the attributes. After he changed the mail attribute he shares, through routing by the IMP server, the IMP client sends an attribute change request message to the connector. The connector does not understand the content of the message but from which relationship it originated from. As the connector cannot notify the system architecture of the service provider, polling for new messages is required. After the system architecture receives the message, it understands the structure of the message and that the purpose of the message is an attribute change request.

The system architecture evaluates if it accepts the changes and sends a response through the REST interface of the connector. The system architecture might execute additional processes. In this case, the mail address stored in the database would be updated.

The IMP server receives the response message through the connector and routes it to the IMP client. The IMP client understands the message, updates the value stored as part of the relationship and displays a notification to the user.

@@

If a user has questions about the newsletter, he can send messages to the service provider as part of the relationship. The client sends the mail message to the IMP server which routes it to the connector. The system architecture polls for incoming messages. When the system architecture receives the message, it understands the content and purpose and for example notifies an employee. An employee could be notified via e-mail and a response from the employee to the mail could automatically be sent to the relationship through the REST API of the connector. Connector and IMP server route the message to the IMP client, who understands the message and displays it to the user.

@@

### 2021-03-04 sections/6-online_access_law.tex
added second integration
message chapter started

In order to save investments a method called "one for all" is used when hosting administrative services. One member state or the federal republic provide access to a service on their administration portal and distribute the requests to the responsible institutions "under the hood". As administration portals are connected through an "online gateway", each portal contains a search feature, which enables users to find all administrative services through any portal. Interoperable user profiles enable usage of each profile for management of administrative services on all portals.

\subsection{Basic Use Case}
The BMI lists a total of almost 600 administrative services, each being described by a different process \cite{BMI:Informatiosplattform}. Each process consists of multiple sub-processes. When comparing the processes, one can see, that some sub-processes occur very often and in similar arrangements. Those arrangements can be called the basic use case of OZG services.

@@

\subsection{System Architecture}
This subsection describes the system architecture of a member state relevant for the execution the basic use case of the OZG based on the system architecture of Nordrhein-Westfalen. Systems, which are responsible for coordination of OZG execution between member states and the federal republic are not the focus.

@@

\begin{figure}[h]
\caption{Overview IMP System}
    \centering
    \includegraphics[scale=0.25]{Diagrams/OZG System Overview.png}
\end{figure}

\paragraph{Administration Portal}
The administration portal is the component which directly interacts with users through a web site an provides the basic OZG use case through interaction with other system components. Through the web page of the portal, the user can create and manage his user profile, receive and send messages, upload and download documents, find administrative services, select an application form for an administrative service and be forwarded to the respective form server. Without direct visibility for the user, the portal also transmits personal information from the user profile to the form server, receives finished applications from the form server, determines responsible institutions and submits applications to the data exchange platform.
The administration portal consists of a web server, responsible for hosting web pages, and a facade for service components. The most important components, the service facade provides an interface for are:

@@

    This service component enables the administration portal to interact with the user profile component to retrieve JSON Web Tokens, update and read personal information and document wallet, to read messages of the inbox and sent messages to an institution.

@@

    This service component manages applications issued through the administration portal through communication with the form server. The component enables the user to start an application by forwarding him to the correct form on the form server and optionally providing personal information to the form server. Form server and portal communicate about the status and content of the application. The user is able to keep track about the status of active applications through the profile, view their content, send messages to responsible institutions and cancel them.

@@

    \textit{Service blocks} contain human readable descriptions about a administrative service.

@@

    \textit{Data fields} are the "smallest entity" of a data field block and describes one standardized piece of information. Depending on the type of information - if it is for example a checkbox or input field - additional metadata is included.

@@

    Each data field block can be uniquely identified through an ID. Therefore, if the form-server is provided with a FIM-ID, he can retrieve the corresponding data filed block from the central storage.

@@

    Depending on the actions of the user, the status of the application changes accordingly and the form server sends an status update.

@@

    The trust level of a logged in user profile is determined while registration and usage. The user can register and login to the user profile using a username / password combination or the German ID card. The trust level "High" is only granted, if the user registered using the German ID card \textbf{AND} logs in using the German ID card. All other combinations of registration and login result in a "normal" trust level.

@@

    The user can attach a copy of a document stored in his data wallet to an application on a from server.

@@

    The user can be notified of a new message through E-Mail.

@@

\subsubsection{Interfaces}
In order to implement the basic use case, the components have to interact with each. The following diagram visualizes, which components interact. Each interaction is described afterwards. The arrows describe the main direction of information flow in an interaction.

\begin{center}
    \includegraphics[width=8cm]{Diagrams/Interaction Diagram.png}
\end{center}

@@

    \item The form-server can initiate the application if requested by the administration portal. The portal submits information for identification, authentication and authorisation of a user through an JSON Web Token and a user profile ID. In order for the form server to determine the correct form to display, the portal submits a FIM-ID which corresponds to a data field schemata. In case the user approved, the portal can also collect personal information from the user profile and submit it to the form server for automated filling in of the form.

>>>>

In order to save investments a method called "one for all" is used when hosting administrative services. One member state or the federal republic provides access to a service on their administration portal and distributes the requests to the responsible institutions "under the hood". As administration portals are connected through an "online gateway", each portal contains a search feature, which enables users to find all administrative services through any portal. Interoperable user profiles enable usage of each profile for management of administrative services on all portals.

\subsection{Basic Use Case}
The BMI lists a total of almost 600 administrative services, each being described by a different process \cite{BMI:Informatiosplattform}. Each process consists of multiple sub-processes. When comparing the processes, one can see that some sub-processes occur very often and in similar arrangements. Those arrangements can be called the basic use case of OZG services.

@@

\subsection{System Architecture}
This subsection describes the system architecture of a member state relevant for the execution of the basic use case of the OZG based on the system architecture of Nordrhein-Westfalen. Systems responsible for coordination of OZG execution between member states and the federal republic are not the focus.

@@

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/OZG System Overview.pdf}
\end{center}

\paragraph{Administration Portal}
The administration portal is the component which directly interacts with users through a web site an provides the basic OZG use case through interaction with other system components. Through the web page of the portal, the user can create and manage his user profile, receive and send messages, upload and download documents, find administrative services, select an application form for an administrative service and be forwarded to the respective form server. Without direct visibility for the user, the portal also transmits personal information from the user profile to the form server, receives finished applications from the form server, determines responsible institutions and submits applications to the data exchange platform.
The administration portal consists of a web server, responsible for hosting web pages, and a facade for service components. The most important components the service facade provides an interface for are:

@@

    This service component enables the administration portal to interact with the user profile component to retrieve JSON Web Tokens, update and read personal information and document wallet, to read messages of the inbox and send messages to an institution.

@@

    This service component manages applications issued through the administration portal through communication with the form server. The component enables the user to start an application by forwarding him to the correct form on the form server and optionally providing personal information to the form server. Form server and portal communicate about the status and content of the application. The user is able to keep track of the status of active applications through the profile, view their content, send messages to responsible institutions and cancel them.

@@

    \textit{Service blocks} contain human readable descriptions about an administrative service.

@@

    \textit{Data fields} are the "smallest entity" of a data field block and describe one standardized piece of information. Depending on the type of information - if it is for example a checkbox or input field - additional metadata is included.

@@

    Each data field block can be uniquely identified through an ID. Therefore, if the form-server is provided with a FIM-ID, he can retrieve the corresponding data field block from the central storage.

@@

    Depending on the actions of the user, the status of the application changes accordingly and the form server sends a status update.

@@

    The trust level of a logged in user profile is determined while registration and usage. The user can register and login to the user profile using a username / password combination or the German ID card. The trust level "High" is only granted if the user registered using the German ID card \textbf{AND} logs in using the German ID card. All other combinations of registration and login result in a "normal" trust level.

@@

    The user can attach a copy of a document stored in his data wallet to an application on a form server.

@@

    The user can be notified of a new message through e-mail.

@@

\subsubsection{Interfaces}
In order to implement the basic use case, the components have to interact with each other. The following diagram visualizes, which components interact. Each interaction is described afterwards. The arrows describe the main direction of information flow in an interaction.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Interaction Diagram.pdf}
\end{center}

@@

    \item The form-server can initiate the application if requested by the administration portal. The portal submits information for identification, authentication and authorisation of a user through a JSON Web Token and a user profile ID. In order for the form server to determine the correct form to display, the portal submits a FIM-ID which corresponds to a data field schemata. In case the user approved, the portal can also collect personal information from the user profile and submit it to the form server for automated filling in of the form.

### 2021-03-04 sections/9-imp_utilization_in_ozg.tex
textualizing
message chapter started

Like many online self-service platforms, the system architecture responsible for implementing the OZG relies on user profiles for managing identities. In case of the OZG, identity management is especially complicated due to the federated model of interoperable user profiles. Each member state has to provide its own user profile system which can be utilized through every administration portal. This solution is expensive to develop and maintain, as communication between multiple member states and institutions is required.

Goal of the integration solution is to introduce features of the IMP system into the OZG system architecture. All existing services should be accessible the same way as before but with additional options for using IMP. The focus of this initial integration is to avoid disruption of existing system operation through non-invasive integration, to enable a fast and simple introduction of IMP features and to provide future upgrade capabilities. The integration takes place on three layers:

\begin{figure}[h]
\caption{IMP Layer Diagram}
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.png}
\end{figure}

\paragraph{IMP Solution Integration Layer} 
The purpose of the integration on the IMP solution layer is to take advantage of new interaction capabilities with the user through the IMP system. The integration evaluates possibilities of using relationships and IMP messages to improve OZG services, defines what the purpose of each message and relationship type is and how they should be handled by client and service provider. For example relationship templates can be defined and new message types can be created with corresponding new user interfaces in the IMP client.

\paragraph{Relationship Integration Layer} The purpose of the integration on the relationship layer is to enable the technological utilization of relationships as described by the integration on the solution integration layer.

\paragraph{Communication Integration Layer} The purpose of the integration on the communication layer is to enable the technological utilization of messages as described by the integration on the solution integration layer.

>>>>

This chapter presents an IMP solution which solves issues of OZG identity management described in chapter 3. For utilization of IMP services as described by the IMP solution, an integration architecture is presented which enables the OZG system architecture described in section 2.3 to access the IMP system described in section 2.2.

Focus of the IMP solution and the integration architecture is to require minimal invasion into the existing system architecture: Few existing system components should have to be modified and the existing operation of the system should not be disrupted. The IMP solution should provide an additional but optional way for users to access OZG services.

The integration takes place on three layers:

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.pdf}
\end{center}

\paragraph{IMP Solution Layer} 
The IMP solution is integration on the use case level. It presents possibilities of leveraging interaction capabilities of the IMP system in the context of the service provider for improvement of usability, data protection and security. It describes which types of relationships the service provider can use in his business scenario, how relationships can be processed, which types of messages can be exchanged trough the relationships, what the purpose of each message can be and how the IMP client can react to different message types.

The IMP solution focuses on utilizing IMP capabilities in a way which affects the existing operation of the system architecture the least while solving as many identity management issues described in section 3.1 as possible.

\paragraph{Technological Integration} 
The technological integration is integration on the system level. It consists of an integration architecture enabling the existing systems of the service provider to utilize the IMP system as described by the IMP solution. It is separated into a "Communication Integration Layer" and a "Relationship to Identity Integration Layer". On the "Relationship to Identity Integration Layer" the integration architecture enables the existing systems to create relationship templates and establish relationships. On the "Communication Integration Layer" it enables the existing systems to send and receive different types of IMP messages.

Focus of the technological integration is to connect with as few existing systems as possible while solving as many integration issues described in section 3.3 as possible.
